Supplementary Material

### 2022-08-05 supplement.tex
Update to customized Figure S1
Update figure caption

% Figure S1 - Outlet Line Submersion
\begin{figure}
    \includegraphics[width=\textwidth]{FigureS1.png}
    \caption {
        Impact of submerging the outlet tubing after the phantom, shown for both flow control systems at 2.4 mm/s and 4.8 mm/s. These trials show approximately five-minute duration of the outlet tubing dripping into the outlet vial (seen by rapid flow drops), followed by five-minute duration of the outlet tubing submerged in solution. The baseline was set to either 2.4 mm/s (left) or 4.8 mm/s (right), using the average $\tau_{c}$ from each respective approximately five-minute duration flow profile after submerging the outlet tubing. The horizontal and vertical axes are the same across all plots. The 3 mL, 4.8 mm/s plot shows a zoomed view of the final drop in the dashed box, where the duration is 11.6 seconds.
    }
    \label{fig:supplement_outlet}
\end{figure}

>>>>

% Figure S1 - Outlet Line Submersion
\begin{figure}
    \includegraphics[width=\textwidth]{FigureS1.pdf}
    \caption {
        Impact of submerging the microfluidic device outlet tubing for both flow control systems at 2.4 and 4.8 mm/s as measured with the inline flow sensor (blue) and single-exposure LSCI (red). These trials show approximately five minutes of effluent dripping into the collection vial, as evidenced by the rapid periodic flow drops, followed by approximately five minutes of operation with the outlet tubing submerged in solution. All measurements were normalized to the average flow during the submerged segment of each experiment and compared to the ideal flow (black).
    }
    \label{fig:supplement_outlet}
\end{figure}
